Synchronizing Distributed Openflow Controllers\\{\Large Toward More Powerful In-Band Synchronization Objects

### 2015-03-11 inband-STN.tex
some fixes and adding groups as a forth feature

The Openflow standard (as of \textbf{TODO}) offers three interesting
features which we will exploit to implement the transactional memory abstraction:

@@

\item \textbf{Conditional Application:}
The Openflow standard also supports the \emph{conditional} application of
certain types of control messages. A specific $\textsf{OFPFF\_CHECK\_OVERLAP}$ flag
set in the control message containing a new forwarding rule ensures
that the rule is applied if and only if it does not \emph{conflict}
with any other rule currently in the flow table.
This in-band conflict detection mechanism, combined with bundling,
allows us to implement specific types of \emph{transactions} that may
atomically install multiple rules if certain compatibility conditions
are met.

\item \textbf{Cookies:} Cookies allow to name and retrieve individual
flow rules. Our synchronization mechanism will implement controller-specific cookies.
\end{enumerate}

>>>>

The Openflow standard (as of \textbf{TODO}) offers four interesting
features which we will exploit to implement the transactional memory abstraction:

@@

\item \textbf{Conditional Application:}
The Openflow standard also supports the \emph{conditional} creation of
flow entries. A specific $\textsf{OFPFF\_CHECK\_OVERLAP}$ flag
set in the flow creation message ensures
that the flow entry is created if and only if it does not \emph{conflict}
with any other flow entry currently in the flow table.
This ?????in-band????? conflict detection mechanism, combined with bundling,
allows us to implement specific types of \emph{transactions} that may
atomically install multiple rules if certain compatibility conditions
are met.

\item \textbf{Cookies:} Cookies allow to name and retrieve individual
flow entries and to use masks to delete modify/delete multiple entries. Our synchronization mechanism will implement controller-specific cookies.

\item \textbf{Groups:} Groups of action buckets can be defined in a special group table. Each group has a unique id and any attempt to create a group with existing id or to delete un existing group fails (and can abort a bundle in process).
\end{enumerate}
